---
title: "An Introduction to ggplot2"
output: learnr::tutorial

runtime: shiny_prerendered
---

```{r setup, include=FALSE}
require(learnr)
require(reshape2)
require(patchwork)
require(ggplot2)
require(knitr)

time_series <- read.csv("data/time_series.csv")
age_data <- read.csv("data/age.csv")
conditions <- read.csv("data/conditions.csv")
TIME_SERIES_FV <- time_series[,c(1,2)]
Melt_Time_Series <- melt(time_series, id.vars= c("Week"))
Melt_Cond_Series <- melt(conditions, id.vars= c("Conditions"))

options(width = 10)
knitr::opts_chunk$set(echo = FALSE)
```

## Preamble (Skip if needed)

In the interest of time and simplicity, I have already installed the necessary packages and the data-sets that you will need to use this workbook. But if you would like to know how I did this, then read the section.

Remember, you only need to download and install the package once. Then when you start a new project, you just need to add library() at the top of the your script and it should work.

```{r echo=TRUE}
#These are commented so they won't run, but you can see the two functions necessary for running packages.

#install.packages('ggplot2')
#install.packages('reshape2')
#install.packages('patchwork')

#library(reshape2)
#library(ggplot2)
#library(patchwork)

```

```{r include=FALSE}

### aha you sneak, you're reading the source code
require(reshape2)
require(patchwork)
require(ggplot2)
require(packrat)
require(knitr)
```

Now, this is how you load in data. This again has already been done for you, but you can see three .csv files and I use the read.csv() here.

```{r echo=TRUE}

time_series <- read.csv("data/time_series.csv")
age_data <- read.csv("data/age.csv")
conditions <- read.csv("data/conditions.csv")


```

## A. A single line plot {data-progressive="TRUE"}

The first step is to look a our data! Here, we have the number of new cases across different counties across time (weeks). We have 4 counties!

```{r echo=FALSE, results='asis'}
kable(head(time_series),caption='The case numbers of TBA')
```

I want to start out very simple, however, and plot cases for a single county. Specifically, I am interested in the time series of the county FV. From the main data-frame (labeled: **time_series**), I want to extract the week column and the Cases_FV column. This corresponds to the first and second column.

```{r echo=TRUE}
#Here, I am extracting the first and second column of the data.frame and assigning it to a new variable which I call TIME_SERIES_FV
TIME_SERIES_FV <- time_series[,c(1,2)]
```

```{r include=FALSE}

TIME_SERIES_FV <- time_series[,c(1,2)]

```
### Exercise A.1: The Data Layer {data-progressive="TRUE"}

*Fill in the blank: the data, the variables within the data that will correspond to the x-axis and the y-axis.*

```{r beginning, exercise=TRUE}
#The data.frame is called TIME_SERIES_FV and the column names are Week and Cases_FV

ggplot(___, aes(x=___ ,y =___ ))
```

### Exercise A.2: The Geom Layer {data-progressive="TRUE"}

*Fill in the blank: Add in the geometric layer, specifically the line-layer (**geom_line**). Finally, add in the point layer (**geom_point**).*

```{r geom_layer, exercise=TRUE}
ggplot(TIME_SERIES_FV, aes(x=Week ,y =Cases_FV ))+
  ____
```

### Exercise A.3: Changing color and size

*Fill in the blank: Change the color of the line to blue and change the size of the point to 2.*

```{r geom_layer_color, exercise=TRUE}
ggplot(TIME_SERIES_FV, aes(x=Week ,y =Cases_FV ))+
  geom_line(_____)+geom_point(______)
```

### Exercise A.4: Changing the appearance with theme

*Fill in the blank: Add the theme layer specifically **theme_bw()***

```{r geom_layer_theme, exercise=TRUE}
ggplot(TIME_SERIES_FV, aes(x=Week ,y =Cases_FV ))+
  geom_line(color='blue')+geom_point(size =3)+
  ______
```

## B. Multiple lines in a plot {data-progressive="TRUE"}

Now let's tackle something a bit harder, let's think about showing all counties in a single line plot.

### Exercise B.1: Melt the data! {data-progressive="TRUE"}

*Fill in the blank: Melt the data.frame from wide to long.*

```{r melt, exercise=TRUE}
#The data.frame is time_series and the variable names are Week, Cases_FV, Cases_I, Cases_CM, Cases_HB

Melt_Time_Series <- melt(_______, id.vars=c("______"))


print(head(Melt_Time_Series))
```

```{r include=FALSE}
Melt_Time_Series <- melt(time_series, id.vars= c("Week"))
```

### Exercise B.2: Plotting the melted data.frame

*Fill in the blank: the data, the variables within the data that will correspond to the x-axis and the y-axis. Add the geom_line*

```{r melt_first_layer, exercise=TRUE}

#Remember the dataframe name is: Melt_Time_Series and the column names are: Week, variable, value

ggplot(_______, aes(x=_____ ,y =_____ ))+________
```

### Exercise B.3: Plotting the melted data.frame again

*Fill in the blank: Fix the graph!*

```{r melt_first_layer_fix, exercise=TRUE}
ggplot(Melt_Time_Series , aes(x=Week ,y =value, _______)+geom_line()
```

### Exercise B.4: Changing the colors manually

*Fill in the blank: Change the scales so that*

1.  *The name of the legend will be Counties*

2.  *The new labels are: FV, I, CM, HB*

3.  *The corresponding new colors are: purple, green, navy, and gold*

```{r melt_first_layer_color, exercise=TRUE}
ggplot(Melt_Time_Series , aes(x=Week ,y =value, color =variable ))+geom_line()+scale_color_manual(name='______',
                      labels = c(__________),
                      values = c(___________))
```

### Exercise B.5: Adding the labels

*Fill in the blank: Change so that the x-axis title is "Week", the y-axis title is "Cases", and the main title is "Time Series of TBA"*

```{r melt_first_layerfinal, exercise=TRUE}
ggplot(Melt_Time_Series , aes(x=Week ,y =value, color =variable ))+geom_line()+scale_color_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+_____+_____+______
```

### Exercise B.6: Adding the theme

*Fill in the blank: add theme_bw()*

```{r melt_first_layer_theme, exercise=TRUE}
ggplot(Melt_Time_Series , aes(x=Week ,y =value, color =variable ))+geom_line()+scale_color_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+xlab("week")+ylab("Cases")+
  ggtitle(("Time Series of TBA"))+____________
```

### Exercise B.7: Facet

*Fill in the blank: add the facet layer and facet by variable (counties)*

```{r melt_first_layer_theme_facet, exercise=TRUE}
ggplot(subset(Melt_Time_Series,Melt_Time_Series$variable != 'Cases_FV'),
              aes(x=Week ,y =value, color =variable ))+geom_line()+ facet_wrap(________)+ 
  scale_color_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+xlab("week")+ylab("Cases")+ggtitle(("Time Series of TBA"))+theme_bw()
```

### Exercise B.8: Multiplot

*Fill in the blank: add the facet layer and facet by counties*

```{r patched, exercise=TRUE}

plot1<-ggplot(Melt_Time_Series , aes(x=Week ,y =value, color =variable ))+geom_line()+ facet_wrap(~variable)+ 
  
  scale_color_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+xlab("week")+ylab("Cases")+ggtitle(("Time Series of TBA"))+theme_bw()

plot2<-ggplot(Melt_Time_Series , aes(x=Week ,y =value, color =variable ))+geom_line()+
  scale_color_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+xlab("week")+ylab("Cases")+ggtitle(("Time Series of TBA"))+theme_bw()


______+_______
_____/______
```

## C. Bargraphs {data-progressive="TRUE"}

```{r echo=FALSE, results='asis'}
kable(head(age_data),caption='The cases by age')
```

### Exercise C.1: Melt Bargraph

*Fill in the blank: Melt the data.frame from wide to long*

```{r bargraph_melt, exercise=TRUE}
#the data is age_data and the columns are Age, FV_Cases, I_Cases,CM_Case, HB_Cases

age_2 <- melt(______, id.vars = c("____"))

View(age_2)
```

```{r include=FALSE}
age_2 <- melt(age_data, id.vars = c('Age'))
```

### Exercise C.2: Data Layer

*Fill in the blank: the data, the variables within the data that will correspond to the x-axis and the y-axis.*

```{r bargraph_data, exercise=TRUE}

###The data.frame we want to use is age_2 and the column names are: Age, variable, and value


ggplot(______, aes(x = ______ , y= _______))

```

### Exercise C.3: Geom Layer

*Fill in the blank: the geographic representation in this case, a barplot (**geom_bar**). (hint do not worry if it does no work the first time)*

```{r bargraph_data_geom, exercise=TRUE}
ggplot(age_2, aes(x = Age , y= value)) + ________
```

### Exercise C.4: Fill Layer

*Fill in the blank: the fill*

```{r bargraph_data_fill, exercise=TRUE}

ggplot(age_2, aes(x = Age , y= value, fill=_______)) + geom_bar(stat=_______)
```

### Exercise C.5: Position

*Fill in the blank: the position*

```{r bargraph_data_position, exercise=TRUE}

ggplot(age_2, aes(x = Age , y= value, fill = variable))+ geom_bar(stat='identity',position=___)
```

### Exercise C.6: Scale Fill

*Fill in the blank: Change the scales so that*

1.  *The name of the legend will be Counties*

2.  *The new labels are: FV, I, CM, HB*

3.  *The corresponding new colors are: purple, green, navy, and gold*

```{r bargraph_data_fill_scale, exercise=TRUE}

ggplot(age_2, aes(x = Age , y= value, fill = variable)) + geom_bar(stat='identity',position='dodge')
  scale_butt_manual(name="",
                     labels=c(),
                     values=c())
```

### Exercise C.7: Labels and theme

*Fill in the blank: Change the x-xis label to "Age", the y-axis label to "Cases" and the main title to "Cases by Age". Finally add in theme_bw()*

```{r bargraph_data_lab, exercise=TRUE}

ggplot(age_2, aes(x = Age , y= value, fill = variable)) + geom_bar(stat='identity',position='dodge')+
    scale_fill_manual(name="Counties",
                     labels=c("FV","I","CM",'HB'),
                     values=c("purple","green","navy",'gold'))+______+______+___________+______
```

## D. Geom Tile {data-progressive="TRUE"}

```{r echo=FALSE, results='asis'}
kable(head(conditions),caption='Conditions')
```

### Exercise D.1: Melt! {data-progressive="TRUE"}

*Fill in the blank: Melt the data.frame from wide to long*

```{r melt_c, exercise=TRUE}
#the data is conditions and the columns are Conditions,FV,	I,	VM,	HB

Melt_Cond_Series <- melt(_______, id.vars=c("_______"))
print(head(Melt_Cond_Series))
```

```{r include=FALSE}
Melt_Cond_Series <- melt(conditions, id.vars= c("Conditions"))
```

### Exercise D.2: Plotting the melted data.frame

*Fill in the blank: the data, the variables within the data that will correspond to the x-axis and the y-axis.*

```{r melt_plo_c, exercise=TRUE}

###The data.frame we want to use is  Melt_Cond_Series  and the column names are: Conditions, variable, value

ggplot(Melt_Cond_Series, aes(x = ______ , y= ______))
```

### Exercise D.3: Geom layer

*Fill in the blank: the geographic representation in this case, a tiled plot (**geom_tile**) and make sure the fill-color is based on the yes or no.*

```{r melt_plot_c_geom, exercise=TRUE}

ggplot(Melt_Cond_Series, aes(x = variable, y= Conditions, fill= ____))+_____
```

### Exercise D.4: Geom layer-color

*Fill in the blank: make the outlines of the tile white*

```{r melt_plot_c_geom_2, exercise=TRUE}

ggplot(Melt_Cond_Series, aes(x = variable, y= Conditions, fill=variable))+geom_tile(color=___)
```

### Exercise D.5: Change the scale-layer

*Fill in the blank: Change the scales so that*

1.  *The name of the legend will be empty ''*

2.  *The new labels are: 'Absent','Present*

3.  *The corresponding new colors are: 'black' and 'green'*

```{r melt_plot_c_geom_3, exercise=TRUE}

ggplot(Melt_Cond_Series, aes(x = variable, y= Conditions, fill=value))+geom_tile(color="white")+
   scale_fill_manual(name = '______',labels = c(_______), values = c(_______))+theme_bw()
```

### Exercise D.6: Change the labels and the theme

*Fill in the blank: Change the x-xis label to "Counties", the y-axis label to "Conditions and the main title to "Are these things present?". Finally add in theme_bw()*

```{r melt_plot_c_geom_4, exercise=TRUE}

ggplot(conditions_2, aes(x = variable, y = Conditions , fill = value))+
  geom_tile(color='white')+
  scale_fill_manual(name = '',labels = c('Absent', "Present"), values = c("black",'green'))+
 xlab(___)+ylab(___)+ggtitle(___)
```
